---
title: "MSBR 70200 Assignment: Reporting using RStudio"
author: "Chamroeun Chhay"
date: "08/26/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

* * *

>`R Markdown (RMD)` is a preferred reporting tool in `R` environment. This assignment is to help you understand how to use R Markdown. 

>Introduce yourself by revising this file (`RMD` file) according to the instruction. To see the formatted report, **knit** this `RMD` file by pressing **Ctrl+Shift+K** for Windows or **Command+Shift+K** for Mac. Notice that how `R Markdown` converts plain texts to formatted texts.

**Helpful Resources**

  * R for Data Science Chapters 1 and 27
  * Reporting with R Markdown (DataCamp)


<br>

* * *


### Basic Formatting Exercises (1 point each)

<br>

#### 1. (Regular text) Briefly introduce yourself. Include your hometown in **BOLD** and hobby in *Italic*.
(1 paragraph)

My name is Chamroeun Chhay. I am from **Phnom Pehn, Cambodia**. My hobbies include *hiking, gaming and cooking*.


<br>

#### 2. (Numbered list) My favorite colors 

1. *Red*
2. *White*


<br>

#### 3. (Bulleted list) My hobbies 

* *Cooking*
* *Hiking*


<br>

#### 4. (Table) Courses taken related to Mathematics, Statistics, and Computer Science
Please fill the following table.

| Course | Level (Under/Grad) | 
| Calculus I | Under |
| Quantitative Business Analysis | Under | 
| Business Analytics | Under | 
| Management Information System | Under |


<br>


* * *

### Use `R` in `RMD` (2 points each)

<br>

> `RMD` is most powerful combined with `R`. The following are simple examples of how to include `R` code and results in RMD.

#### 6. In RMD file, `R` code should be inside `R` code chunk. Follow each step to show the result.

  a. Create a `R` code chunk, press Ctrl+Alt+I in Windows or Cmd+Alt+I in Mac. 
  b. Write R code to compute $\frac{0.99 \times 0.5}{0.01+0.098 \times 0.50}$.
  c. After knitting this file, you should be able to obtain the answer, 0.99.

<br>

```{r}
(0.99*0.5)/(0.01+0.98*0.50)
    
```


<br>


#### 7. Recall `cars` data set in your first `R` Markdown.

  a. Create a `R` code chunk, press Ctrl+Alt+I in Windows or Cmd+Alt+I in Mac. 
  b. Write R code to draw scatter plot with `speed` as x-axis and `dist` as y-axis. (Hint: Recall how your first RMD drew a scatter plot.)

<br>

```{r}
summary(cars)
plot(cars)

```

<br>


 * * *
 * * *
 
## Submission

1. Once you answer all questions, save this file as `MSBR_70200_Assignment_RMD_FirstName_LastName.rmd` with your first and last names.
2. Then, knit this rmd file by pressing Ctrl+Shift+K in Windows or Command+Shift+K in Mac.
3. Submit the knitted html file to Canvas.

* To get the full score, you should follow the formatting guidelines, if any. All of your `R` code should be inside `R` code chunk. 